### 2016-09-30 architecture.tex
Better wording

Listing~\ref{fig:gamma-example} presents an example of extensibility in SymPy.
It gives a minimal version of the gamma function $\Gamma(x)$ from SymPy, which
evaluates itself on positive integer arguments, has the real assumption
defined, can be rewritten in terms of factorial with
\verb|gamma(x).rewrite(factorial)|, and can be differentiated.
\texttt{self.func} is used throughout instead of referencing \texttt{gamma}
explicitly so that potential subclasses of \texttt{gamma} can reuse the
methods.

>>>>

Listing~\ref{fig:gamma-example} presents an example of this extensibility. It
gives a stripped down version of the \texttt{gamma} function $\Gamma(x)$ from
SymPy. The methods defined allow it to evaluate itself on positive integer
arguments, define the real assumption, allow it to be rewritten in terms of
factorial (with \verb|gamma(x).rewrite(factorial)|), and allow it to be
differentiated. \texttt{self.func} is used throughout instead of referencing
\texttt{gamma} explicitly so that potential subclasses of \texttt{gamma} can
reuse the methods.
